MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-27 paper.Rmd
Added ScienceDirect reference.

Energy flowing through societal energy conversion chains (ECCs)
enables economic activity and facilitates human flourishing.
To understand economic growth and human well-being, 
the field of societal energy analysis (among other activities)
evaluates ECCs
from the primary stage 
(resources extracted from the environment, 
such as coal, oil, and natural gas) 
to the final stage
(energy purchased by consumers, 
such as refined petroleum and electricity),
to the useful stage
(energy desired by the end user, 
such as heat, motion, and light),
and sometimes to energy services
(such as thermal comfort, transport, and illumination).
Societal exergy analysis (SEA), 
an extension of energy analysis,
quantifies ECCs in exergy terms^[Exergy is 
the mechanical work potential of energy.].

>>>>

Energy flowing through societal energy conversion chains (ECCs)
enables economic activity and facilitates human flourishing.
To understand economic growth and human well-being, 
the field of societal energy analysis (among other activities)
evaluates ECCs
from the primary stage 
(resources extracted from the environment, 
such as coal, oil, and natural gas) 
to the final stage
(energy purchased by consumers, 
such as refined petroleum and electricity),
to the useful stage
(energy desired by the end user, 
such as heat, motion, and light),
and sometimes to energy services
(such as thermal comfort, transport, and illumination).
Societal exergy analysis (SEA), 
an extension of energy analysis,
quantifies ECCs in exergy terms^[Exergy is 
the mechanical work potential of energy.
See any number of web references for an exergy primer,
including @SciDirect:2023].
